Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-08-16 Presentations/YESconference.tex

\normalsize Related studies find that well educated workers exited at higher rates due to computerization \tiny (Willis and Hudomiet 2021, Labour), (Dillender & Forsythe 2022, NBER)
\end{frame}

@@

\begin{frame}{Retirement: Senior Physicians}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_retire_old.pdf}
\end{figure}
$\rightarrow$ 25\% increase relative to the mean in the first year, but 0 in the second\\
$\rightarrow$ What does this mean for younger physicians?
\end{frame}

>>>>

\normalsize Related studies find that well educated workers exited at higher rates due to computerization \tiny (Willis and Hudomiet 2021, Labour), (Dillender \& Forsythe 2022, NBER)
\end{frame}

@@

\begin{frame}{Retirement: Senior Physicians}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_retire_ages.pdf}
\end{figure}
$\rightarrow$ 25\% increase relative to the mean in the first year, but 0 in the second\\
$\rightarrow$ What does this mean for younger physicians?
\end{frame}
